---
title: "Harry Potter and the Rvest of Fan Fiction"
author: "Liza Bolton for R Ladies Auckland"
date: "May 22, 2018"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

## Set up
We're going to need a package called `rvest` (rvest, harvest, geddit?) to do our web scraping, `robotstxt` helps with some of our ethics checking, and `stringr`and `dplyr` will help with our data cleaning.

```{r set-up, message=FALSE, warning=FALSE}

# install.packages("dplyr")
# install.packages("ggplot2")
# install.packages("lubridate")
# install.packages("purrr")
# install.packages("readr")
# install.packages("robotstxt")
# install.packages("rvest")
# install.packages("stringr")
# install.packages("tidyr")

library(dplyr)
library(ggplot2)
library(lubridate)
library(purrr)
library(readr)
library(robotstxt)
library(rvest)
library(stringr)
library(tidyr)

```

In your browser, you can got to [https://www.fanfiction.net/robots.txt](www.fanfiction.net/robots.txt), or check what it says directly from your R session!
```{r ethics, warning=FALSE}

rt = robotstxt("fanfiction.net")

# Check which areas are off limits
rt$permissions

# Any mention of a crawl delay?
rt$crawl_delay

```


```{r scrape-data}

# Pick which page you want to scrape - This URL takes stories of all ratings, sorted by favourites as a measure of popularity
base_url = 
  "https://www.fanfiction.net/book/Harry-Potter/?&srt=4&r=10&p="

# 1:20 indicates the pages I want
# There are 25 stories per page, so the first 20 pages gives us the top 500 stories
map_df(1:20, function(i) {

  pages = read_html(paste0(base_url, i))
  
  # The '.' before stitle and xgray indicates that it is the class
  data.frame(title = html_text(html_nodes(pages, ".stitle")), details=html_text(html_nodes(pages, ".xgray")),
             stringsAsFactors=FALSE)

}) -> data

# Store how many stories for each graph titles later
n_stories = dim(data)[1]

```

## Get some helpful information from the filter menu
This next section pulls some information from the filters menu to help up clean up the data later. See [this xpath tutorial](https://www.w3schools.com/xml/xpath_intro.asp) for more information.

```{r helpful-bits}
# Major credit to Anna for this code and the chunk below - you would have been disgusted by how hack-y it was before

home = read_html("https://www.fanfiction.net/book/Harry-Potter/")

# Get genres
genres = home %>% 
  html_nodes(xpath='//*[@id="myform"]/div[1]/select[3]/option') %>%
  html_text() 
genres = genres[-1] #delete first text value
genresReg = paste(genres, collapse = '|')

# Get the list of characters
characters <- home %>% 
  html_nodes(xpath='//*[@id="myform"]/div[1]/select[10]/option') %>%
  html_text() 
charactersReg = paste(characters, collapse = '|')

# Get ratings
ratingLevels <- c("K", "K+", "T", "M")

# Useful for later
my_counter = function(x){
 return(length(x) - sum(str_detect(x, "Not")))
}

```

## Tidy up the data
```{r tidy-data}

tidy_data = data %>%
  mutate(id = 1:n()) %>%
  select(id,title, details) %>% 
  separate_rows(details,sep="- ") %>%
  separate(details,c("varName", "tempValue"), sep=":", fill="left") %>%
  mutate(
    newValue = str_trim(tempValue),
    newVarName = case_when(
      !is.na(varName) ~ varName,
      str_detect(newValue, "Complete") ~ "Completed",
      str_detect(newValue, genresReg) ~ "Genres",
      str_detect(newValue, charactersReg) ~ "Characters",
      TRUE ~ "Language"
    )
  ) %>% 
  select(id, title, newVarName, newValue) %>%
  spread(newVarName, newValue, fill = NA) %>%
  mutate_at(vars(c("Chapters","Favs","Follows","Reviews","Words")), parse_number) %>%
  mutate_at(vars(c("Published")), mdy) %>%
  mutate(
    Rating = factor(Rated, ratingLevels),
    Completed = case_when(is.na(Completed) ~ "Not complete", 
                          TRUE ~ "Complete"),
    Characters = str_replace_all(Characters,c("\\[" = "","\\]" = ""))
  )

# Make columns for each genre

for (ii in 1:length(genres)){
    tidy_data = tidy_data %>%
    mutate_(.dots = setNames(list(paste0("case_when(str_detect(Genres, \"", genres[ii], "\") ~ \"", genres[ii], "\",
                                        TRUE ~ paste0(\"Not \", \"", genres[ii], "\"),
                                        NA ~ paste0(\"Not \",\"", genres[ii], "\"))"
                                        )), paste0("genre_", genres[ii])))
}

# Make columns for each character
# This one takes a while because there are a lot of characters that could be included

for (jj in 1:length(characters)){
    tidy_data = tidy_data %>%
    mutate_(.dots = setNames(list(paste0("case_when(str_detect(Characters, \"", characters[jj], "\") ~ \"", characters[jj], "\",
                                        TRUE ~ paste0(\"Not \", \"", characters[jj], "\"),
                                        NA ~ paste0(\"Not \",\"", characters[jj], "\"))"
                                        )), paste0("character_", characters[jj])))
}


```

## Fun stuff - let's get plottin'!
```{r fun-stuff-genres}
# See how many stories featuring each character there are 

# Set how many stories minimum they must appear in to be included
appear_lim = 0
summary_genre = tidy_data %>% 
  select(starts_with("genre_")) %>% 
  sapply(my_counter) %>% 
  data.frame() %>% 
  rename_(Counts = names(.)[1]) %>% 
  mutate(Genre = str_split_fixed(rownames(.), "genre_", 2)[,2]) %>% 
  filter(Counts>=appear_lim) %>% 
  arrange(desc(Counts)) %>% 
  ggplot(aes(x = reorder(Genre, -Counts), y = Counts)) +
  geom_bar(stat = "identity", fill="#611c64") +
  xlab("Genres") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle(paste("Genre popularity among stories in the top", n_stories)) +
  geom_text(stat='identity', aes(label=Counts), vjust=-0.3)

summary_genre

```


```{r fun-stuff-characters}
# See how many stories featuring each character there are 

# Set how many stories minimum they must appear in to be included
appear_lim = 5
summary_character = tidy_data %>% 
  select(starts_with("character_")) %>% 
  sapply(my_counter) %>% 
  data.frame() %>% 
  rename_(Counts = names(.)[1]) %>% 
  mutate(Character = str_split_fixed(rownames(.), "character_", 2)[,2]) %>% 
  filter(Counts>=appear_lim) %>% 
  arrange(desc(Counts)) %>% 
  ggplot(aes(x = reorder(Character, -Counts), y = Counts)) +
  geom_bar(stat = "identity", fill="#611c64") +
  xlab("Characters") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  ggtitle(paste("Characters that appear in at least", appear_lim, "stories in the top", n_stories)) +
  geom_text(stat='identity', aes(label=Counts), vjust=-0.3)

summary_character


  
```

```{r fun-stuff-rating}

rating = tidy_data %>% 
  ggplot(aes(Rating)) +
  geom_bar(fill="#611c64") +
  ylab("Count") +
  theme_minimal() +
  ggtitle(paste("Ratings of stories in the top", n_stories)) +
  geom_text(stat='count', aes(label=..count..), vjust=-0.3)
  
rating

```

```{r fun-stuff_rating_romance}

rating_romance = tidy_data %>% 
  ggplot(aes(Rating, fill=genre_Romance)) +
  geom_bar() +
  ylab("Count") +
  theme_minimal() +
  ggtitle(paste("Romance stories in each rating group in the top", n_stories)) +
  scale_fill_discrete(name = "Romance genre")
  
rating_romance

```

```{r fun-stuff_rating_males}

male_ratings = data_frame("Harry P." = xtabs(~`character_Harry P.`+Rating, data=tidy_data)[1,],
      "Draco M." = xtabs(~`character_Draco M.`+Rating, data=tidy_data)[1,],
      "Severus S." = xtabs(~`character_Severus S.`+Rating, data=tidy_data)[2,],
      "Sirius B." = xtabs(~`character_Sirius B.`+Rating, data=tidy_data)[2,],
      "Ron W."= xtabs(~`character_Ron W.`+Rating, data=tidy_data)[2,],
      "Voldemort" = xtabs(~`character_Voldemort`+Rating, data=tidy_data)[2,]) %>% 
  gather(Character, Rating_Count) %>% 
  mutate(Rating = factor(rep(ratingLevels, 6), levels = c("K", "K+", "T", "M")))

ggplot(male_ratings, aes(Character, Rating_Count, fill=Rating)) +
  geom_bar(stat="identity", position = "fill") +
  ylab("Proportion") +
  ggtitle(paste0("Which of these male characters has the greatest proportion of the stories \nthey're featured in (in the top ", n_stories, ") rated Mature?")) +
  theme_minimal()

```
```{r fun-stuff-numeric}

scatterplot = tidy_data %>% 
  filter(Published > 2000) %>% 
  mutate(Publish_cat = case_when(
    year(Published) < 2006 ~ "2002 - 2005",
    year(Published) < 2010 ~ "2006 - 2009",
    year(Published) < 2014 ~ "2010 - 2013",
    TRUE ~ "2014 - 2017"
  )) %>% 
  ggplot(aes(x = Chapters, y = Favs, color = Completed)) +
  geom_point() +
  facet_grid(. ~ Publish_cat) +
  theme_minimal() +
  scale_color_discrete(name = "Completed") +
  ggtitle("Favourites and chapters by publishing date and completion status", subtitle = paste0("Top ", n_stories, " stories by number of favourites"))
  
scatterplot

```

