---
title: "Harry Potter and the Rvest of Fan Fiction"
author: "Liza Bolton for R Ladies Auckland"
date: "May 22, 2018"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Kia ora! Ko Liza tōku ingoa.
* PhD student in Statistics, University of Auckland 
    + Official statistics, social/economic patterns and mortality in New Zealand
* Data Ambassador <a href=www.dataembassy.co.nz>www.dataembassy.co.nz</a>
* Sometimes an Introduction to Statistics lecturer
    + From which the example in this workshop comes from
* Harry Potter fan
* Canadian
* Twitter: <a href="https://twitter.com/Liza_Bolton">@LizaBolton</a>

## What are we doing today?
* What is web scraping?
* What do we need to know to do it ethically?
    + robots.txt
    + APIs
* Very simple intro to HTML and CSS
* Stats 10x Harry Potter fanfiction case study
* Your turn!

# Webscraping 
## What is web scraping?


## What do we need to know to do it ethically? | So even Hermione Grange would approve

# Stats 10x Harry Potter fanfiction case study

## Why Harry Potter fanfiction?
* Why not?
* This great post by Shirley Wu was an early inspiration http://sxywu.com/hpff/

## Taking a look at FanFiction.net

https://www.fanfiction.net/

## Set up

Install the <monowidth>rvest()</monowidth> package as well as two very useful tidyverse packages.
```{r}
# install.packages(rvest)
# install.packages(stringr)
# install.packages(dplyr)

library(rvest)
library(stringr)
library(dplyr)

%>% 
```



#All Harry Potter Fanfic
# Store web url
i = sample(1:29076, 10)
urls = paste0("https://www.fanfiction.net/book/Harry-Potter/?&srt=4&r=10&p=", i)

for(j in 1:4){
test <- read_html(urls[j])
#Scrape the website for the movie rating
info[(1:25)+(j-1)*25] = test %>% 
  html_nodes(".xgray") %>%
  html_text()
}
info

sampledinfo = info[sample(length(info), 100)]
rating_lang = str_split_fixed(sampledinfo, " - ", n=12)[,c(1,2)]
genre = str_split_fixed(sampledinfo, " - ", n=12)[,3]
genre[grep("Chapters", genre)] = NA
chapter = str_split_fixed(sampledinfo, "Chapters: ", n=2)[,2]
chapter =  str_split_fixed(chapter, " - ", n=2)[,1]
words = str_split_fixed(sampledinfo, "Words: ", n=2)[,2]
words = str_split_fixed(words, " - ", n=2)[,1]
reviews = str_split_fixed(sampledinfo, "Reviews: ", n=2)[,2]
reviews = str_split_fixed(reviews, " - ", n=2)[,1]
favs = str_split_fixed(sampledinfo, "Favs: ", n=2)[,2]
favs = str_split_fixed(favs, " - ", n=2)[,1]
follows = str_split_fixed(sampledinfo, "Follows: ", n=2)[,2]
follows = str_split_fixed(favs, " - ", n=2)[,1]
final = str_split_fixed(sampledinfo, "Published: ", n=2)[,2]
final = str_split_fixed(final, " - ", n=3)
published = final[,1]
characters = final[,2]
characters[grep("Complete", characters)] = NA
complete = final[,3]
complete[grep("Complete", characters)]="Complete"

cleaned = data.frame(rating_lang, genre, chapter, words, reviews, favs, follows, published, characters, complete)
View(cleaned)
write.csv(cleaned, "generalsample.csv")

#Dramione
# Store web url
i = sample(1:156, 10)
urls = paste0("https://www.fanfiction.net/book/Harry-Potter/?&srt=1&r=10&c1=3&c2=6&pm=1&p=", i)

for(j in 1:4){
  test <- read_html(urls[j])
  #Scrape the website for the movie rating
  info[(1:25)+(j-1)*25] = test %>% 
    html_nodes(".xgray") %>%
    html_text()
}
info

sampledinfo = info[sample(length(info), 100)]
rating_lang = str_split_fixed(sampledinfo, " - ", n=12)[,c(1,2)]
genre = str_split_fixed(sampledinfo, " - ", n=12)[,3]
genre[grep("Chapters", genre)] = NA
chapter = str_split_fixed(sampledinfo, "Chapters: ", n=2)[,2]
chapter =  str_split_fixed(chapter, " - ", n=2)[,1]
words = str_split_fixed(sampledinfo, "Words: ", n=2)[,2]
words = str_split_fixed(words, " - ", n=2)[,1]
reviews = str_split_fixed(sampledinfo, "Reviews: ", n=2)[,2]
reviews = str_split_fixed(reviews, " - ", n=2)[,1]
favs = str_split_fixed(sampledinfo, "Favs: ", n=2)[,2]
favs = str_split_fixed(favs, " - ", n=2)[,1]
follows = str_split_fixed(sampledinfo, "Follows: ", n=2)[,2]
follows = str_split_fixed(favs, " - ", n=2)[,1]
final = str_split_fixed(sampledinfo, "Published: ", n=2)[,2]
final = str_split_fixed(final, " - ", n=3)
published = final[,1]
characters = final[,2]
characters[grep("Complete", characters)] = NA
complete = final[,3]
complete[grep("Complete", characters)]="Complete"

cleaned = data.frame(rating_lang, genre, chapter, words, reviews, favs, follows, published, characters, complete)
View(cleaned)
write.csv(cleaned, "dramione.csv")

#Drarry
# Store web url
i = sample(1:151, 10)
urls = paste0("https://www.fanfiction.net/book/Harry-Potter/?&srt=1&r=10&c1=1&c2=6&pm=1&p=", i)

for(j in 1:4){
  test <- read_html(urls[j])
  #Scrape the website for the movie rating
  info[(1:25)+(j-1)*25] = test %>% 
    html_nodes(".xgray") %>%
    html_text()
}
info

sampledinfo = info[sample(length(info), 100)]
rating_lang = str_split_fixed(sampledinfo, " - ", n=12)[,c(1,2)]
genre = str_split_fixed(sampledinfo, " - ", n=12)[,3]
genre[grep("Chapters", genre)] = NA
chapter = str_split_fixed(sampledinfo, "Chapters: ", n=2)[,2]
chapter =  str_split_fixed(chapter, " - ", n=2)[,1]
words = str_split_fixed(sampledinfo, "Words: ", n=2)[,2]
words = str_split_fixed(words, " - ", n=2)[,1]
reviews = str_split_fixed(sampledinfo, "Reviews: ", n=2)[,2]
reviews = str_split_fixed(reviews, " - ", n=2)[,1]
favs = str_split_fixed(sampledinfo, "Favs: ", n=2)[,2]
favs = str_split_fixed(favs, " - ", n=2)[,1]
follows = str_split_fixed(sampledinfo, "Follows: ", n=2)[,2]
follows = str_split_fixed(favs, " - ", n=2)[,1]
final = str_split_fixed(sampledinfo, "Published: ", n=2)[,2]
final = str_split_fixed(final, " - ", n=3)
published = final[,1]
characters = final[,2]
characters[grep("Complete", characters)] = NA
complete = final[,3]
complete[grep("Complete", characters)]="Complete"

cleaned = data.frame(rating_lang, genre, chapter, words, reviews, favs, follows, published, characters, complete)
View(cleaned)
write.csv(cleaned, "drarry.csv")

#Hinny
# Store web url
i = sample(1:62, 10)
urls = paste0("https://www.fanfiction.net/book/Harry-Potter/?&srt=1&r=10&c1=1&c2=11&pm=1&p=", i)

for(j in 1:4){
  test <- read_html(urls[j])
  #Scrape the website for the movie rating
  info[(1:25)+(j-1)*25] = test %>% 
    html_nodes(".xgray") %>%
    html_text()
}
info

sampledinfo = info[sample(length(info), 100)]
rating_lang = str_split_fixed(sampledinfo, " - ", n=12)[,c(1,2)]
genre = str_split_fixed(sampledinfo, " - ", n=12)[,3]
genre[grep("Chapters", genre)] = NA
chapter = str_split_fixed(sampledinfo, "Chapters: ", n=2)[,2]
chapter =  str_split_fixed(chapter, " - ", n=2)[,1]
words = str_split_fixed(sampledinfo, "Words: ", n=2)[,2]
words = str_split_fixed(words, " - ", n=2)[,1]
reviews = str_split_fixed(sampledinfo, "Reviews: ", n=2)[,2]
reviews = str_split_fixed(reviews, " - ", n=2)[,1]
favs = str_split_fixed(sampledinfo, "Favs: ", n=2)[,2]
favs = str_split_fixed(favs, " - ", n=2)[,1]
follows = str_split_fixed(sampledinfo, "Follows: ", n=2)[,2]
follows = str_split_fixed(favs, " - ", n=2)[,1]
final = str_split_fixed(sampledinfo, "Published: ", n=2)[,2]
final = str_split_fixed(final, " - ", n=3)
published = final[,1]
characters = final[,2]
characters[grep("Complete", characters)] = NA
complete = final[,3]
complete[grep("Complete", characters)]="Complete"

cleaned = data.frame(rating_lang, genre, chapter, words, reviews, favs, follows, published, characters, complete)
View(cleaned)
write.csv(cleaned, "Hinny.csv")

#hermioneron
# Store web url
i = sample(1:62, 10)
urls = paste0("https://www.fanfiction.net/book/Harry-Potter/?&srt=1&r=10&c1=3&c2=2&pm=1&p=", i)

info=NULL
for(j in 1:4){
  test <- read_html(urls[j])
  #Scrape the website for the movie rating
  info[(1:25)+(j-1)*25] = test %>% 
    html_nodes(".xgray") %>%
    html_text()
}
info

sampledinfo = info[sample(length(info), 100)]
rating_lang = str_split_fixed(sampledinfo, " - ", n=12)[,c(1,2)]
genre = str_split_fixed(sampledinfo, " - ", n=12)[,3]
genre[grep("Chapters", genre)] = NA
chapter = str_split_fixed(sampledinfo, "Chapters: ", n=2)[,2]
chapter =  str_split_fixed(chapter, " - ", n=2)[,1]
words = str_split_fixed(sampledinfo, "Words: ", n=2)[,2]
words = str_split_fixed(words, " - ", n=2)[,1]
reviews = str_split_fixed(sampledinfo, "Reviews: ", n=2)[,2]
reviews = str_split_fixed(reviews, " - ", n=2)[,1]
favs = str_split_fixed(sampledinfo, "Favs: ", n=2)[,2]
favs = str_split_fixed(favs, " - ", n=2)[,1]
follows = str_split_fixed(sampledinfo, "Follows: ", n=2)[,2]
follows = str_split_fixed(favs, " - ", n=2)[,1]
final = str_split_fixed(sampledinfo, "Published: ", n=2)[,2]
final = str_split_fixed(final, " - ", n=3)
published = final[,1]
characters = final[,2]
characters[grep("Complete", characters)] = NA
complete = final[,3]
complete[grep("Complete", characters)]="Complete"

cleaned = data.frame(rating_lang, genre, chapter, words, reviews, favs, follows, published, characters, complete)
View(cleaned)
write.csv(cleaned, "hermioneron.csv")



dramione = read.csv("dramione.csv")
drarry = read.csv("drarry.csv")
hinny = read.csv("hinny.csv")
romione = read.csv("hermioneron.csv")

dramione$ship = "dramione"
dramione$shipnum = 1
drarry$ship = "drarry"
drarry$shipnum = 2
hinny$ship = "hinny"
hinny$shipnum = 3
romione$ship = "romione"
romione$shipnum = 4

all = data.frame(rbind(dramione, drarry, hinny, romione))
all$favs = as.numeric(all$favs)

write.csv(all, "all.csv")

mod = lm(all$fav ~ all$ship, data=all)
summary(mod)
confint(mod)



```



## Your turn
